This document represents a synthetic study of the work carried out during my third-year internship. I completed my internship at the University of Paris Est Créteil (\textbf{UPEC}) and the company Exakis Nelite (\textbf{EXN}), a collaborator with Microsoft. This internship lasted three months, from late April to late July 2024. The main objective of this project was to develop a tool and a web interface for the management, configuration, and audit of Microsoft and Azure cloud environments, often collectively referred to as "tenant." The project was carried out in three main stages:
\begin{itemize}
\item[•] Detailed needs analysis;
\item[•] Design of the various components of the application;
\item[•] Implementation of the defined objectives.
\end{itemize}

I had the opportunity to utilize a variety of technologies, tools, and concepts that greatly contributed to the realization of this solution. Among these resources, several were drawn from the courses I took over the previous year, thus consolidating my theoretical knowledge. Additionally, I discovered and learned to master new tools during my training within the company, which allowed me to acquire additional practical skills. You will find a detailed summary of these technologies and tools used in the appendices of this document.

This report is structured to provide a clear and detailed overview of the entire project. Chapter I is dedicated to the presentation of the host organization, including the introduction to the team and the company, as well as the definition of the internship objectives. Chapter II focuses on the functional framework and project presentation, detailing the benchmark of available solutions, and the conceptual study of needs and security standards. Chapter III addresses the technical framework, where the various technical components of the proposed solution are developed, including the analysis of the existing setup, initial uses, and customization of the MONKEY365 solution. Finally, Chapter IV is devoted to the realization part, where I will discuss my concrete achievements during the internship, such as obtaining certifications, introduction to DevOps, building applications with Azure DevOps, participating in a Microsoft event on new AI technologies, and the development and deployment of a website serving as a personal portfolio, highlighting the specific contributions I made to the project.

\textbf{\\Keywords:\\ Management, Configuration, Audit, Microsoft, Azure cloud, Tenant, Design, Appendix, Technology.}